---
title: "Introduction"
description: |
  A conceptual introduction to Bayesian data analysis, workflow, and a first model
author:
  - name: Matti Vuorre
    url: https://vuorre.netlify.com
    affiliation: University of Oxford
    affiliation_url: https://www.oii.ox.ac.uk/people/matti-vuorre/
    orcid_id: 0000-0001-5052-066X
date: 2020-10-22
bibliography: bibliography.bib
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = TRUE, fig.align = 'center'
)
```

## Slide deck

Click [here](slides.html) to go to the slide deck.

```{r embed-xaringan, layout="l-body-outset"}
xaringanExtra::embed_xaringan(url = "slides.html", ratio = "4:3")
```

## Recommended reading

The three books cited in this lesson are all highly recommended readings. For beginners to Bayesian statistics, I recommend starting with Kruschke [-@kruschke2014], or McElreath [-@mcelreath2020]. Bayesian Data Analysis by Gelman et al. [-@gelman2013] is the definitive textbook on the topic, and recommended for more mathematically oriented and/or advanced readers.

-   "Bayesian evaluation of behavior change interventions: a brief introduction and a practical example" [@heino2018] ([pdf](https://vuorre.netlify.app/publication/2018/01/01/bayesian-evaluation-of-behavior-change-interventions-a-brief-introduction-and-a-practical-example/heino-bayesianevaluationbehavior-2018.pdf))

```{r bayesian-inference, preview=TRUE}
library(tidyverse)
library(scales)
x <- seq(0, 1, by = .001)
a1 <- 3; a2 <- 6; b1 <- 10; b2 <- 4
Prior <- dbeta(x, a1, a2)
Likelihood <- dbeta(x, b1, b2)
Posterior <- dbeta(x, a1+b1, a2+b2)
tibble(x, Prior, Likelihood, Posterior) %>% 
  pivot_longer(-x) %>% 
  mutate(name = factor(name, levels = c("Prior", "Likelihood", "Posterior"), labels = c(~italic(p)(theta), ~italic(p)(Y~"|"~theta), ~italic(p)(theta~"|"~Y)))) %>% 
  ggplot(aes(x, value, col = name, fill = name)) +
  scale_colour_viridis_d("", aesthetics = c("color", "fill"), direction = -1) +
  scale_y_continuous(expand = expansion(c(0, .1))) +
  scale_x_continuous("Parameter value", breaks = pretty_breaks()) +
  geom_ribbon(aes(ymin = 0, ymax = value), size = 0, alpha = .8) +
  facet_wrap(
    "name", strip.position = "left", labeller = label_parsed
    ) +
  theme(
    legend.position = "none",
    aspect.ratio = 1,
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks = element_blank()
    )
```
